Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
changes to targeting specific pluggable transports bullet

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others don't.
Also, some of them require additional information
(like bridge addresses) before they can work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports?

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?
